Highly Available Transactions: Virtues and Limitations

### 2013-03-31 writeup/relatedwork.tex
checkpoin

From Serializable to Causal Transactions for Collaborative Applications: Causal consistency with lost update

Middleware-based Database Replication: The Gaps Between Theory and Practice
Most uses Snapshot Isolation

@@

, with increasing interest in returning to transactional
designs~\cite{spanner, walter, foundation-article, krikellas-bargain,
  eiger}

>>>>

@@

%, with increasing interest in returning to transactional
%designs~\cite{spanner, walter, foundation-article, krikellas-bargain,
%  eiger}
